### 2022-03-30 conclusion/conclusion.tex
more

In Chapter \ref{ch:ho-techniques} we only scratched the surface of finding the
appropriate heuristics. Now that \ehohii{} implements more advanced higher-order
reasoning it would be interesting to verify that our heuristics are agnostic of
the version of implemented higher-order superposition calculus.

>>>>

In Chapter \ref{ch:ho-techniques} we only scratched the surface of finding the
appropriate heuristics. Now that \ehohii{} implements more advanced higher-order
reasoning it would be interesting to verify that heuristics that are still not ported are agnostic of
the version of implemented higher-order superposition calculus.
